---
title: "Homework 5"
author: "Govind Rachapudi: gr25925"
date: "2024-02-21"
output: html_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(mosaic)
library(stringr) 
```

## Problem 1 - Iron Bank

```{r, echo=FALSE, warning=FALSE, message=FALSE}
sim_trades <- do(100000)*nflip(n = 2021, prob = .024)
#head(sim_trades)
```

Step 1: The null hypothesis is that there is no difference in the flagging rate between Iron Bank trades and trades from other banks.

Step 2: The test statistic is the amount of trades that are flagged out of total trades. For instance, 70 out of 2021.

```{r,echo=FALSE,message=FALSE,warning=FALSE}
ggplot(sim_trades)+
  geom_histogram(aes(x=nflip), binwidth = 1, fill = "indianred3", color = "black")
#the p value is the probability of something out of the norm in accordinance with the data occurring. 
p_val <- sum(sim_trades >= 70)/100000
#p_val

```

Step 4: The P value is approximately .0020.

Conclusion: According to the data, the null hypothesis proves to be false since the probably of 70 trades being flagged out of 2021 is .0020. This p value indicates that the null hypothesis can be rejected and assumes that it is false.

## Problem 2

Step 1: There is no difference in the rate of health code violations for Gourmet Bites and average rate of health code violations for restaurants citywide.

Step 2: The test statistic in this case is the number of health code violations that restaurants such as Gourmet Bites receive. For instance, 8 out of 50.

```{r, echo=FALSE, warning=FALSE, message=FALSE}

sim_inspection <- do(100000)*nflip(n = 1500, prob = .03)
ggplot(sim_inspection)+
  geom_histogram(aes(x=nflip), binwidth = 1, fill = "coral3", color = "black")
p_value <- sum(sim_inspection >= 50)/100000
#p_value

```

Step 3: The P value is .2455

Step 4: In conclusion, we would fail to reject the null hypothesis since the P-value is much greater than 0.05. The rate of health code violations at Gourmet Bites is significantly different from the average rate of 3%.

## Problem 4

#### Part A

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#null distribution
library(stringr)
sentences <- readLines("brown_sentences.txt")
letter_frequencies <- read.csv("letter_frequencies.csv")

#sentence processing
process <- function(sentence){
  sentence <- gsub("[^A-Z]", "", toupper(sentence))
  observed_counts <- rep(0,26)
  names(observed_counts) <- LETTERS
  counts <- table(str_split(sentence, "")[[1]])
  observed_counts[names(counts)] <- counts
  expected_counts <- letter_frequencies$Probability * nchar(sentence) + 0.1
  chi_squaretest <- sum((observed_counts-expected_counts)^2 / expected_counts)
  p_value <- 1-pchisq(chi_squaretest, 25)
  return(chi_squaretest)
}

chi_values <- sapply(sentences, process)
summary(chi_values)

sentence_data <- data.frame(results = chi_values)
ggplot(sentence_data, aes(x = results))+
  geom_histogram(fill = "cornflowerblue", color = "black")+
  labs(title = "Distribution of Chi-Squared Values", 
       x = "Chi-Squared Value",
       y = "Frequency")+
  theme_bw()
```

The Summary table above represents the range of chi-square values that you can expect to see in normal English sentences.

#### Part B: checking for a watermark

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(kableExtra)
test_sentences <- c(
  "She opened the book and started to read the first chapter, eagerly anticipating what might come next.",
  "Despite the heavy rain, they decided to go for a long walk in the park, crossing the main avenue by the fountain in the center.",
  "The museum’s new exhibit features ancient artifacts from various civilizations around the world.",
  "He carefully examined the document, looking for any clues that might help solve the mystery.",
  "The students gathered in the auditorium to listen to the guest speaker’s inspiring lecture.",
  "Feeling vexed after an arduous and zany day at work, she hoped for a peaceful and quiet evening at home, cozying up after a quick dinner with some TV, or maybe a book on her upcoming visit to Auckland.",
  "The chef demonstrated how to prepare a delicious meal using only locally sourced ingredients, focusing mainly on some excellent dinner recipes from Spain.",
  "They watched the sunset from the hilltop, marveling at the beautiful array of colors in the sky.",
  "The committee reviewed the proposal and provided many points of useful feedback to improve the project’s effectiveness.",
  "Despite the challenges faced during the project, the team worked tirelessly to ensure its successful completion, resulting in a product that exceeded everyone’s expectations."
)

pval_generator <- function(sentence){
  sentence <- gsub("[^A-Z]", "", toupper(sentence))
  observed_counts <- rep(0,26)
  names(observed_counts) <- LETTERS
  counts <- table(str_split(sentence, "")[[1]])
  observed_counts[names(counts)] <- counts
  expected_counts <- letter_frequencies$Probability * nchar(sentence) +0.1
  chi_squaretest <- sum((observed_counts-expected_counts)^2 / expected_counts)
  p_value <- 1-pchisq(chi_squaretest, 9)
  return(p_value)
}
p_values <- sapply(test_sentences, pval_generator)
#summary(p_values)
p_values_table <- data.frame(P_Value = round(p_values, digits = 3))
watermarked <- min(p_values_table)
#watermarked

kable(p_values_table, format = "html", align = "c", caption = "P-Values for Sentences") %>% 
  kable_styling(full_width = FALSE)
```

That sentence that is watermarked is "Feeling vexed after an arduous and zany day at work, she hoped for a peaceful and quiet evening at home, cozying up after a quick dinner with some TV, or maybe a book on her upcoming visit to Auckland." This is because the p value for this sentence is extremely low (.000000005), which indicates that it almost entirely rejects the null hypothesis.
